Data Analysis

### 2022-09-02 04.manuscript_scopus.Rmd
edits and clean up

---
title             : "Who does big team science?"
shorttitle        : "Big Team Science"

author: 
  - name          : "Erin M. Buchanan"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "326 Market St., Harrisburg, PA 17101"
    email         : "ebuchanan@harrisburgu.edu"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Data curation
      - Formal Analysis
      - Methodology
      - Project administration
      - Visualization
      - Writing – original draft
      - Writing – review & editing
  - name          : "Savannah C. Lewis"
    affiliation   : "2"
    role:
      - Conceptualization
      - Data curation
      - Methodology
      - Project administration
      - Writing – original draft
      - Writing – review & editing
affiliation:
  - id            : "1"
    institution   : "Harrisburg University of Science and Technology"
  - id            : "2"
    institution   : "University of Alabama"

authornote: |
  Erin M. Buchanan is a Professor of Cognitive Analytics at Harrisburg University of Science and Technology. Savannah C. Lewis is a graduate student at the University of Alabama.

  Thank you to Dwayne Lieck for providing an extensive list of large scale projects for this manuscript.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

@@

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "big team, science, authorship, credit"
wordcount         : "X"

#bibliography      : ["big_team_refs.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

@@

science collaboration overall (sav)
  - what is collaboration
  - is it increasing 
  - globalization should help

@@

- definition for big team size: 10 authors + at least 10 different institutions
- we will use all categories but break into the big four: https://service.elsevier.com/app/answers/detail/a_id/14882/supporthub/scopus/~/what-are-the-most-frequent-subject-area-categories-and-classifications-used-in/ 
- we would get everything from df_ani 
- only use 1970 and forward

@@

journal information we could include:
  - total number of articles overall 
  - number of distinct journals in each of the four areas 
  - JIF df_sources, snip
  - https://liu.cwp.libguides.com/c.php?g=45770&p=4417804

@@

- keywords are easier now - could use the ASJC smaller subfield areas to create a list 
- https://service.elsevier.com/app/answers/detail/a_id/15181/supporthub/scopus/
- table of all the codes

@@

**_Career Length_**. Career length for each author was defined using multiple variables to see if results from the two data sources would converge on similar answers. Both ORCID and Google Scholar provide a list of publications for authors, and we first calculated career length as the year of first publication listed for each author. In ORCID, a researcher can enter their educational background with completion years for each degree. We defined career length for this variable as years since first degree listed. Publication years are often curated directly from meta-data provided by Crossref (ORCID) or online sources used by Google Scholar. Authors may also directly add publications and their information into both systems. The limitation to using education as a metric for career length is that the researcher must directly enter this information into ORCID.

@@

**_Employment_**. Employment information was collected from self-entered ORCID data. These values are open text, and therefore, we coded them into coherent categories for traditional educational (graduate student, post doctoral, lecturer),  tenure track (assistant, associate, full professor), and other roles (fellow, research assistant, researcher, head). Employment geopolitical region was also selected when available.

@@

**_Education_**. As with employment information, we also collected education information from self-entered ORCID data. These values were coded into general categories of bachelor, master, and doctoral degrees. The geopolitical region of the listed education was included when available. For analyses, both employment and education levels were grouped into United Nation regions.

@@

**_Types of Publications_**. ORCID includes information about the type of publication pulled from either researcher entered data or Crossref. We coded these publications into general categories including book, conference presentations, data-sets, journal articles, preprints, software, thesis, and other publications.

@@

**_Publication Metrics_**. We calculated total number of publications of any type from both Google Scholar and ORCID. We additionally pulled both the h-index and i-10 index from Google Scholar. The h-index represents the highest *h* number of publications that have at least *h* citations, while the i-10 index represents the number of publications with at least 10 citations.

@@

### RQ3: Authors. \

We will use $\alpha$ < .05 for all analyses that involve hypothesis testing. We make no directional predictions.

**_Career Length_**. For each of the three variables in career length (ORCID year of first pub, Scholar year of first pub, ORCID year of first degree), we will create a visualization of the trend and variance of researcher career length across publication years. To analyze trends over time, we will use the slope from a multilevel model (MLM) using the individual as a random intercept, career length as the dependent variable, and year of publication as the predictor variable. MLMs are regression models that control for the correlated error due to the repeated and nested nature of the data [CITE]. In this model, each individual's starting career length is arbitrary, which we allow to vary with the random intercept by participant. A positive slope for year of publication would indicate increasing years of first publication (i.e., more younger scholars over time), while a negative slope would indicate older years of first publication (i.e., more older scholars over time). In order to show variance between individuals, we will report the variance component of the random intercept for individuals. Finally, to examine variance over time, we will calculate the standard deviation of the individual within each publication (i.e., one standard deviation for each article), and use a linear model with year predicting these standard deviations. This model is a traditional simultaneous regression, as averaging the variance by title eliminates the repeated measures variable (individuals). A positive slope would indicate increasing variance over time (i.e., more diversity in the career lengths of scholars), while a negative slope would indicate less variance and diversity in scholars over time.

@@

**_Employment_**. We will summarize the general employment categories of individuals at the time of publication, along with a summary for change over time. 
**_Education_**. We will summarize the general education categories of individuals at the time of publication, along with a summary for change over time.

**_Types of Publications_**. We will summarize the coded types of publications for individuals.

**_Publication Metrics_**. We will report descriptive statistics on the total number of publications, i10 index, and h-index for individuals overall. Next, we will use the same analyses described in the career length section to analyze trends over time. An increasing slope over time indicates that individuals who are publishing more are more represented in big-team science over time (i.e., increasing numbers of scholars with higher publication rates), while a negative slope indicates more researchers with less publications. A positive slope for variance indicates increasing variance over time (i.e., more diversity in the individual publication rates), while a negative slope would indicate less diversity in researchers over time. While publication rates do not represent value as a researcher, they are often used in hiring and promotion decisions, and we will use this variable as a proxy to gauge the diversity in scholars represented in big teams. 
same idea average down by paper for mean and standard deviation

**_Geopolitical Regions_**. We will present visualizations of the last listed education and job location, and we will discuss the areas of world in which authors generally come from, as well as the lowest representation of authors. To understand the change in representation diversity, we will summarize the total number of geopolitical regions for each paper. Using a linear model, we will examine if the number of regions present is predicted by the year of publication. Increasing diversity would be represented by a positive slope, while decreasing diversity would be represented by a negative slope. Last, we will examine the differences in representation for corresponding author sets versus all other authors. For papers with 10 to 49 authors, we will use the three first authors and the last author to compare against random samples of other authors. For 50 to 99 authors, five first authors plus last will be used, and for all papers with more than 100 authors, we will use ten first authors and the last author. We will calculate the frequencies of each of the UN Sub-Regions for first authors. Then we will randomly sample all authors in subsets of the same size (i.e., 3+1, 5+1, 10+1), and average the frequencies of UN Sub-Regions across these random samples. We will randomly sample the same number of times as the size of the author list (i.e., a paper that has 54 authors will be randomly sampled 54 times with a sample size of six).

@@

### RQ3: Authors. \

@@

**_Career Length_**. The average career length was `r format(round(current_year - mean(o_works_summary$o_career_1_pub, na.rm = T), digits = 2), nsmall = 2)` (*SD* = `r format(round(sd(current_year - o_works_summary$o_career_1_pub, na.rm = T), digits = 2), nsmall = 2)`) for ORCID first publication year (i.e., current year minus year of first publication), *M* = `r format(round(current_year - mean(s_works_summary$s_career_1_pub, na.rm = T), digits = 2), nsmall = 2)` (*SD* = `r format(round(sd(current_year - s_works_summary$s_career_1_pub, na.rm = T), digits = 2), nsmall = 2)`) for Scholar year of first publication, and *M* = `r format(round(current_year - mean(o_ed_summary$o_career_1_degree, na.rm = T), digits = 2), nsmall = 2)` (*SD* = `r format(round(sd(current_year - o_ed_summary$o_career_1_degree, na.rm = T), digits = 2), nsmall = 2)`) for ORCID year of first degree. In each of the analyses, we use the actual year of first publication/education, as subtracting publication and using it as a predictor would create a perfect solution for each model.

@@

**_Employment_**. Overall, individuals **at the time of publication** in big team science publications are  `r employment_overall$Var1[1]` (`r format(employment_overall$Percent[1], nsmall = 1, digits = 1)`%) and `r employment_overall$Var1[2]` (`r format(employment_overall$Percent[2], nsmall = 1, digits = 1)`%), followed by smaller categories for `r employment_overall$Var1[3]` (`r format(employment_overall$Percent[3], nsmall = 1, digits = 1)`%), `r employment_overall$Var1[4]` (`r format(employment_overall$Percent[4], nsmall = 1, digits = 1)`%), `r employment_overall$Var1[5]` (`r format(employment_overall$Percent[5], nsmall = 1, digits = 1)`%), and `r employment_overall$Var1[6]` (`r format(employment_overall$Percent[6], nsmall = 1, digits = 1)`%). Here, we will talk about the figure below and how the trends occur across time. We will also comment on the number of jobs that would be considered "non-academic".

@@

**_Education_**. Overall, individuals **at the time of publication** in big team science publications are  `r education_overall$Var1[1]` (`r format(education_overall$Percent[1], nsmall = 1, digits = 1)`%), `r education_overall$Var1[2]` (`r format(education_overall$Percent[2], nsmall = 1, digits = 1)`%), and `r education_overall$Var1[3]` (`r format(education_overall$Percent[3], nsmall = 1, digits = 1)`%). Here, we will talk about the figure below and how the trends occur across time.

@@

**_Types of Publications_**. In general, the most common type of publication was `r publication_overall$Var1[1]` (`r format(publication_overall$Percent[1], nsmall = 1, digits = 1)`%), followed by `r publication_overall$Var1[2]` (`r format(publication_overall$Percent[2], nsmall = 1, digits = 1)`%), and smaller categories for `r publication_overall$Var1[3]` (`r format(publication_overall$Percent[3], nsmall = 1, digits = 1)`%), `r publication_overall$Var1[4]` (`r format(publication_overall$Percent[4], nsmall = 1, digits = 1)`%), `r publication_overall$Var1[5]` (`r format(publication_overall$Percent[5], nsmall = 1, digits = 1)`%), and `r publication_overall$Var1[6]` (`r format(publication_overall$Percent[6], nsmall = 1, digits = 1)`%). We will include all information over 1% of the publication totals.

@@

**_Publication Metrics_**. The average number of all publications per individual was *M* = `r format(round(mean(merged_df$o_total_pub, na.rm = T), digits = 2), nsmall = 2)` (*SD* = `r format(round(sd(merged_df$o_total_pub, na.rm = T), digits = 2), nsmall = 2)`) using ORCID and *M* = `r format(round(mean(merged_df$s_total_pub, na.rm = T), digits = 2), nsmall = 2)` (*SD* = `r format(round(sd(merged_df$s_total_pub, na.rm = T), digits = 2), nsmall = 2)`) using Google Scholar. The average i10 index was *M* = `r format(round(mean(merged_df$i10_index, na.rm = T), digits = 2), nsmall = 2)` (*SD* = `r format(round(sd(merged_df$i10_index, na.rm = T), digits = 2), nsmall = 2)`) and the average h-index was *M* = `r format(round(mean(merged_df$h_index, na.rm = T), digits = 2), nsmall = 2)` (*SD* = `r format(round(sd(merged_df$h_index, na.rm = T), digits = 2), nsmall = 2)`).

@@

**_Geopolitical Regions_**. We will first present two figures for education and employment geopolitical regions representation in scholars.

@@

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup

>>>>

---
title             : "Who does big team science?"
shorttitle        : "Big Team Science"
author: 
  - name          : "Erin M. Buchanan"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "326 Market St., Harrisburg, PA 17101"
    email         : "ebuchanan@harrisburgu.edu"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Data curation
      - Formal Analysis
      - Methodology
      - Project administration
      - Visualization
      - Writing – original draft
      - Writing – review & editing
  - name          : "Savannah C. Lewis"
    affiliation   : "2"
    role:
      - Conceptualization
      - Data curation
      - Methodology
      - Project administration
      - Writing – original draft
      - Writing – review & editing
affiliation:

  - id            : "1"
    institution   : "Harrisburg University of Science and Technology"
  - id            : "2"
    institution   : "University of Alabama"
authornote: |
  Erin M. Buchanan is a Professor of Cognitive Analytics at Harrisburg University of Science and Technology. Savannah C. Lewis is a graduate student at the University of Alabama.

  Thank you to Dwayne Lieck for providing an extensive list of large scale projects for this manuscript. 
abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

@@

  <!-- https://tinyurl.com/ybremelq -->
keywords          : "big team, science, authorship, credit"
wordcount         : "X"
#bibliography      : ["big_team_refs.bib"]
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
editor_options: 
  markdown: 
    wrap: 72
bibliography: references.bib
---

@@

According to the Oxford English dictionary, collaboration is two or more
people working together to achieve a certain goal [@oed2016].
Collaboration in scientific endeavors involves multiple researchers at
(potentially) multiple institutions to communicate and work together to
advance knowledge in their chosen field. Collaboration can look
differently in every project dependent on the skill sets, hypotheses,
and perspectives of your collaborators. While collaboration is not new
in science, the current interest of "big team science" is increasing
[@forscher2020; @stewart2017; @coles2022]. Big team science projects
and/or organizations utilize and run on large-scale collaboration to
ensure that diverse populations and ideas are brought into research
projects, which in turn allows for more reliability and generalizability
in the results and method of the study. For this study, Big Team Science
(BTS) will be defined as a collaboration of ten or more authors from at
least ten different institutions.

Big Team Science appears to be increasing as a result of two sources: 1)
increasing globalization and technology that allows for real-time
interdisciplinary research, and 2) increasing interest in
reproducibility, replication, and generalizability [@maxwell2015;
@nelson2018; @zwaan2018]. Technological advances have provided easier
ways to collaborate with people who are from other universities and
countries through document sharing platforms (e.g., Google, GitHub, and
the Open Science Framework), video chatting platforms (e.g., Zoom,
Microsoft Teams), and messaging and project management platforms (e.g.,
Slack, Trello, when2meet, etc.). The credibility movement seems to
suggest that by having both collaborations that span across the globe
and subfield of psychology, age groups and education levels should help
to drive psychological science in the path of better materials,
reliability, generalizability and more robust sample size in a study.
(ADD CITES)

ADD STUFF ABOUT THE CREDIBILITY MOVEMENT HERE....

@@

-   definition for big team size: 10 authors + at least 10 different
    institutions
-   we will use all categories but break into the big four:
    <https://service.elsevier.com/app/answers/detail/a_id/14882/supporthub/scopus/~/what-are-the-most-frequent-subject-area-categories-and-classifications-used-in/>
-   we would get everything from df_ani
-   only use 1970 and forward

@@

journal information we could include: - total number of articles
overall - number of distinct journals in each of the four areas - JIF
df_sources, snip -
<https://liu.cwp.libguides.com/c.php?g=45770&p=4417804>

@@

-   keywords are easier now - could use the ASJC smaller subfield areas
    to create a list
-   <https://service.elsevier.com/app/answers/detail/a_id/15181/supporthub/scopus/>
-   table of all the codes

@@

***Career Length***. Career length for each author was defined using
multiple variables to see if results from the two data sources would
converge on similar answers. Both ORCID and Google Scholar provide a
list of publications for authors, and we first calculated career length
as the year of first publication listed for each author. In ORCID, a
researcher can enter their educational background with completion years
for each degree. We defined career length for this variable as years
since first degree listed. Publication years are often curated directly
from meta-data provided by Crossref (ORCID) or online sources used by
Google Scholar. Authors may also directly add publications and their
information into both systems. The limitation to using education as a
metric for career length is that the researcher must directly enter this
information into ORCID.

@@

***Employment***. Employment information was collected from self-entered
ORCID data. These values are open text, and therefore, we coded them
into coherent categories for traditional educational (graduate student,
post doctoral, lecturer), tenure track (assistant, associate, full
professor), and other roles (fellow, research assistant, researcher,
head). Employment geopolitical region was also selected when available.

@@

***Education***. As with employment information, we also collected
education information from self-entered ORCID data. These values were
coded into general categories of bachelor, master, and doctoral degrees.
The geopolitical region of the listed education was included when
available. For analyses, both employment and education levels were
grouped into United Nation regions.

@@

***Types of Publications***. ORCID includes information about the type
of publication pulled from either researcher entered data or Crossref.
We coded these publications into general categories including book,
conference presentations, data-sets, journal articles, preprints,
software, thesis, and other publications.

@@

***Publication Metrics***. We calculated total number of publications of
any type from both Google Scholar and ORCID. We additionally pulled both
the h-index and i-10 index from Google Scholar. The h-index represents
the highest *h* number of publications that have at least *h* citations,
while the i-10 index represents the number of publications with at least
10 citations.

@@

### RQ3: Authors.

We will use $\alpha$ \< .05 for all analyses that involve hypothesis
testing. We make no directional predictions.

***Career Length***. For each of the three variables in career length
(ORCID year of first pub, Scholar year of first pub, ORCID year of first
degree), we will create a visualization of the trend and variance of
researcher career length across publication years. To analyze trends
over time, we will use the slope from a multilevel model (MLM) using the
individual as a random intercept, career length as the dependent
variable, and year of publication as the predictor variable. MLMs are
regression models that control for the correlated error due to the
repeated and nested nature of the data [CITE]. In this model, each
individual's starting career length is arbitrary, which we allow to vary
with the random intercept by participant. A positive slope for year of
publication would indicate increasing years of first publication (i.e.,
more younger scholars over time), while a negative slope would indicate
older years of first publication (i.e., more older scholars over time).
In order to show variance between individuals, we will report the
variance component of the random intercept for individuals. Finally, to
examine variance over time, we will calculate the standard deviation of
the individual within each publication (i.e., one standard deviation for
each article), and use a linear model with year predicting these
standard deviations. This model is a traditional simultaneous
regression, as averaging the variance by title eliminates the repeated
measures variable (individuals). A positive slope would indicate
increasing variance over time (i.e., more diversity in the career
lengths of scholars), while a negative slope would indicate less
variance and diversity in scholars over time.

@@

***Employment***. We will summarize the general employment categories of
individuals at the time of publication, along with a summary for change
over time. ***Education***. We will summarize the general education
categories of individuals at the time of publication, along with a
summary for change over time.

***Types of Publications***. We will summarize the coded types of
publications for individuals.

***Publication Metrics***. We will report descriptive statistics on the
total number of publications, i10 index, and h-index for individuals
overall. Next, we will use the same analyses described in the career
length section to analyze trends over time. An increasing slope over
time indicates that individuals who are publishing more are more
represented in big-team science over time (i.e., increasing numbers of
scholars with higher publication rates), while a negative slope
indicates more researchers with less publications. A positive slope for
variance indicates increasing variance over time (i.e., more diversity
in the individual publication rates), while a negative slope would
indicate less diversity in researchers over time. While publication
rates do not represent value as a researcher, they are often used in
hiring and promotion decisions, and we will use this variable as a proxy
to gauge the diversity in scholars represented in big teams. same idea
average down by paper for mean and standard deviation

***Geopolitical Regions***. We will present visualizations of the last
listed education and job location, and we will discuss the areas of
world in which authors generally come from, as well as the lowest
representation of authors. To understand the change in representation
diversity, we will summarize the total number of geopolitical regions
for each paper. Using a linear model, we will examine if the number of
regions present is predicted by the year of publication. Increasing
diversity would be represented by a positive slope, while decreasing
diversity would be represented by a negative slope. Last, we will
examine the differences in representation for corresponding author sets
versus all other authors. For papers with 10 to 49 authors, we will use
the three first authors and the last author to compare against random
samples of other authors. For 50 to 99 authors, five first authors plus
last will be used, and for all papers with more than 100 authors, we
will use ten first authors and the last author. We will calculate the
frequencies of each of the UN Sub-Regions for first authors. Then we
will randomly sample all authors in subsets of the same size (i.e., 3+1,
5+1, 10+1), and average the frequencies of UN Sub-Regions across these
random samples. We will randomly sample the same number of times as the
size of the author list (i.e., a paper that has 54 authors will be
randomly sampled 54 times with a sample size of six).

@@

### RQ3: Authors.

@@

***Career Length***. The average career length was
`r format(round(current_year - mean(o_works_summary$o_career_1_pub, na.rm = T), digits = 2), nsmall = 2)`
(*SD* =
`r format(round(sd(current_year - o_works_summary$o_career_1_pub, na.rm = T), digits = 2), nsmall = 2)`)
for ORCID first publication year (i.e., current year minus year of first
publication), *M* =
`r format(round(current_year - mean(s_works_summary$s_career_1_pub, na.rm = T), digits = 2), nsmall = 2)`
(*SD* =
`r format(round(sd(current_year - s_works_summary$s_career_1_pub, na.rm = T), digits = 2), nsmall = 2)`)
for Scholar year of first publication, and *M* =
`r format(round(current_year - mean(o_ed_summary$o_career_1_degree, na.rm = T), digits = 2), nsmall = 2)`
(*SD* =
`r format(round(sd(current_year - o_ed_summary$o_career_1_degree, na.rm = T), digits = 2), nsmall = 2)`)
for ORCID year of first degree. In each of the analyses, we use the
actual year of first publication/education, as subtracting publication
and using it as a predictor would create a perfect solution for each
model.

@@

***Employment***. Overall, individuals **at the time of publication** in
big team science publications are `r employment_overall$Var1[1]`
(`r format(employment_overall$Percent[1], nsmall = 1, digits = 1)`%) and
`r employment_overall$Var1[2]`
(`r format(employment_overall$Percent[2], nsmall = 1, digits = 1)`%),
followed by smaller categories for `r employment_overall$Var1[3]`
(`r format(employment_overall$Percent[3], nsmall = 1, digits = 1)`%),
`r employment_overall$Var1[4]`
(`r format(employment_overall$Percent[4], nsmall = 1, digits = 1)`%),
`r employment_overall$Var1[5]`
(`r format(employment_overall$Percent[5], nsmall = 1, digits = 1)`%),
and `r employment_overall$Var1[6]`
(`r format(employment_overall$Percent[6], nsmall = 1, digits = 1)`%).
Here, we will talk about the figure below and how the trends occur
across time. We will also comment on the number of jobs that would be
considered "non-academic".

@@

***Education***. Overall, individuals **at the time of publication** in
big team science publications are `r education_overall$Var1[1]`
(`r format(education_overall$Percent[1], nsmall = 1, digits = 1)`%),
`r education_overall$Var1[2]`
(`r format(education_overall$Percent[2], nsmall = 1, digits = 1)`%), and
`r education_overall$Var1[3]`
(`r format(education_overall$Percent[3], nsmall = 1, digits = 1)`%).
Here, we will talk about the figure below and how the trends occur
across time.

@@

***Types of Publications***. In general, the most common type of
publication was `r publication_overall$Var1[1]`
(`r format(publication_overall$Percent[1], nsmall = 1, digits = 1)`%),
followed by `r publication_overall$Var1[2]`
(`r format(publication_overall$Percent[2], nsmall = 1, digits = 1)`%),
and smaller categories for `r publication_overall$Var1[3]`
(`r format(publication_overall$Percent[3], nsmall = 1, digits = 1)`%),
`r publication_overall$Var1[4]`
(`r format(publication_overall$Percent[4], nsmall = 1, digits = 1)`%),
`r publication_overall$Var1[5]`
(`r format(publication_overall$Percent[5], nsmall = 1, digits = 1)`%),
and `r publication_overall$Var1[6]`
(`r format(publication_overall$Percent[6], nsmall = 1, digits = 1)`%).
We will include all information over 1% of the publication totals.

@@

***Publication Metrics***. The average number of all publications per
individual was *M* =
`r format(round(mean(merged_df$o_total_pub, na.rm = T), digits = 2), nsmall = 2)`
(*SD* =
`r format(round(sd(merged_df$o_total_pub, na.rm = T), digits = 2), nsmall = 2)`)
using ORCID and *M* =
`r format(round(mean(merged_df$s_total_pub, na.rm = T), digits = 2), nsmall = 2)`
(*SD* =
`r format(round(sd(merged_df$s_total_pub, na.rm = T), digits = 2), nsmall = 2)`)
using Google Scholar. The average i10 index was *M* =
`r format(round(mean(merged_df$i10_index, na.rm = T), digits = 2), nsmall = 2)`
(*SD* =
`r format(round(sd(merged_df$i10_index, na.rm = T), digits = 2), nsmall = 2)`)
and the average h-index was *M* =
`r format(round(mean(merged_df$h_index, na.rm = T), digits = 2), nsmall = 2)`
(*SD* =
`r format(round(sd(merged_df$h_index, na.rm = T), digits = 2), nsmall = 2)`).

@@

***Geopolitical Regions***. We will first present two figures for
education and employment geopolitical regions representation in
scholars.

@@

```{=tex}
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
```
::: {#refs custom-style="Bibliography"}
:::

```{=tex}
\endgroup
```
